---
title: "cowbird"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cowbird}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(cowbird)
```

# `cowbird`: Functions behind the cowbird paper

This package can be used to reproduce the analysis done in the cowbird paper.

## Data 

Use `data('cowbird_data')` to load in the dataset used in the paper.

```{r data}
data('cowbird_data')
head(cowbird_data)
```

Note the misnomer: the `data.frame` contains detection data for the hosts and the cowbird. In addition, it contains one site-level covariate (land_use), and one visit-level covariate (observer_b, a dummy variable identifying the observer at the site). 

`make_data_list()` converts the `data.frame` to a list for use in `rjags`

```{r data_list}
data_list <- make_data_list(cowbird_data)
str(data_list)
```

## Fitting models

There are two ways to fit the models described in the paper: fitting each model individually, or fitting them all at once. 

Either way, `rjags` needs a character vector of parameters whose MCMC samples you would like returned. `get_evaluation_parameters(checking_params = TRUE)` returns a vector of parameters needed to do posterior predictive checks and calculate WAIC.

```{r get_parms}
params <- get_evaluation_parameters(checking_parameters = TRUE)
params
```

### Fit all models

`fit_all_models()` fits each model sequentially and returns a list of output from each model. For speed, I've set the MCMC parameters to very low numbers. 

```{r fit_all}
fit_list <- fit_all_models(
  data_list, 
  params_to_monitor = params,
  n.chains = 1, 
  n.adapt = 100, 
  n.burn = 10,
  n.iter = 10, 
  n.thin = 1
)
```

### Fit one model

`fit_model()` fits one of the models from the paper individually. 

```{r fit_one}
model1_fit <- fit_model(
  'model_1', 
  data_list,
  params_to_monitor = NULL, 
  n.chains = 1, 
  n.adapt = 100, 
  n.burn = 10, 
  n.iter = 10,
  n.thin = 1
)
```

## Checking models

`check_all_models()` performs a posterior predictive check on the model list returned from `fit_all_models()`.

```{r check_all}
ppc <- check_all_models(fit_list, data_list, just_pvals = TRUE)
ppc
```

`check_model()` peforms a posterior predictive check of one model.
